\bf Focusing on Fast Neural Network Inference

### 2018-05-16 wnmt.2018/wnmt.tex
small numerical differences

We take an opposing approach by using and enhancing a custom inference engine, Amun, which is developed on the premise that fast neural network inference is an issue that deserves dedicated tools which are not compromised by other objectives such as training or support for multiple models. As well as delivering on the useful goal of fast inference, it can serve as a test-bed for novel ideas on neural network inference, and is useful as a means to explore the upper limit of the possible speed for a particular model and hardware.

That is, Amun is an inference-only engine that supports a limited number of NMT models that put fast inference on modern GPU above all other consideration. The consequence of this focused approach can be seen in the results of the shared task ???.

@@

The use of mini-batching is critical for fast model inference. However, a percularity

However, mini-batching often does not take into account variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, maxi-batching can introduce unacceptable delay in response for online applications as the input are not processed in the order they came. It is also not appropriate for applications where only the output lengths varies, for example, image captioning.

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Mini-Batching}{}
\While{more input} 
  \State Create batch $b$
  \State Encode($b$)
  \While{batch is not empty} 
    \State Decode($b$)
    \ForAll{sentence $s$ in $b$}
      \If{trans($s$) is complete}
        \State Remove $s$ from $b$
      \EndIf
    \EndFor
  \EndWhile
\EndWhile

@@

\end{document}
\grid

>>>>

We take an opposing approach by using and enhancing a custom inference engine, Amun, which is developed on the premise that fast neural network inference is an issue that deserves dedicated tools which are not compromised by other objectives such as training or support for multiple models. As well as delivering on the useful goal of fast inference, it can serve as a test-bed for novel ideas on neural network inference, and is useful as a means to explore the upper limit of the possible speed for a particular model and hardware. That is, Amun is an inference-only engine that supports a limited number of NMT models that put fast inference on modern GPU above all other considerations. %The consequence of this focused approach can be seen in the results of the shared task ???.

@@

The use of mini-batching is critical for fast model inference. The size of the batch is determined by the number of inputs sentences to the encoder in an encoder-decoder model. However, the number of batches during decoding can vary as some sentences have completed translating or the beam search add more hypotheses to the batch.

It is tempting to ignore these consideration, for example, by always decoding with a constant batch and beam size and ignoring hypotheses which are not needed. This is the strategy taken by other inference engines such as Marian, at the cost of lower translation speed due to wasteful processing.

The Amun engine implements an efficient batching algorithm that takes into account the actual number of hypotheses that needs to be decoded at each decoding step, Figure~\ref{algo:Mini-batching}.

\begin{algorithm}
\begin{algorithmic}
\Procedure{Batching}{encoded records $i$}

\State Create batch $b$ from $i$

\While{$b$ is not empty} 
  \State $b' \gets$ DecodeAndBeamSearch($b$)
  \State $b \gets \emptyset$

  \ForAll{hypo $h$ in $b'$}
    \If{$h \neq \textless/s \textgreater$  }
      \State Add $h$ to $b$
    \EndIf
  \EndFor
\EndWhile

@@

@@

\end{document}
\grid
\grid
